## Exercise (to do at home)

**1- Read in file ex6c_input.txt (that is in folder downloaded for exercice 6 "i_o_files") in object "extra"**
  
  Warning: the file has a header !
  <br>
  Check the structure of extra (remember the **str** command).

<details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
extra <- read.table("i_o_files/ex6c_input.txt", 
                  header=TRUE)
str(extra)
```

</details>
  
  
  **2- Read in the same file but, this time, set the argument as.is to TRUE.**
  
  Check again the structure: what has changed ?
  
  <details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
extra <- read.table("i_o_files/ex6c_input.txt", 
                  header=TRUE,
                  as.is=TRUE)
str(extra)
```

</details>
  
  **3- What are the column names of extra ?**
  
  <details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
colnames(extra)
```

</details>
  
  **4- Change the name of the first column of extra from "State" to "Country".**
  
  <details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
# ex6ct all column names of extra
colnames(extra)
# ex6ct the name of the first column only
colnames(extra)[1]
# reassign name of the first column only
colnames(extra)[1] <- "Country"
```

</details>
  
  **5- How many countries are in the Eurozone, according to extra ?**
  
  *Remember the table function. ?table*
  
  <details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
table(extra$Eurozone)
```

</details>
  
  **6- In the Eurozone column: change "TRUE" with "yes" and "FALSE" with "no".**
  
  <details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
# select the Eurozone column
extra$Eurozone
# elements of the Eurozone column that are exactly TRUE
extra$Eurozone==TRUE
# ex6ct actual values that are TRUE
extra$Eurozone[extra$Eurozone==TRUE]
# reassign all elements that are TRUE with "yes"
extra$Eurozone[extra$Eurozone==TRUE] <- "yes"
# same with FALSE
extra$Eurozone[extra$Eurozone==FALSE] <- "no"
```

</details>
  
  **7- In the column Country: how many country names from the list contain the letter "c" (capital- or lower-case) ?**
  
  Remember the grep function. Check the help page.

<details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
# country names with "c" (lower-case)
grep("c", extra$Country)
# country names with "c" or "C" (ignoring case)
grep("c", extra$Country, ignore.case = TRUE)
# show actual country names
grep("c", extra$Country, value=TRUE, ignore.case = TRUE)
```

</details>
  
  **8- According to that data frame: how many people live:**
  + in the European union (whole table) ?
  + in the Eurozone ?
  
  <details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
# sum the whole population column
sum(extra$Population)
# select elements of extra where Eurozone is "yes"
extra$Eurozone == "yes"
# select only elements in Population for which the corresponding Eurozone elements are "yes"
extra$Population[extra$Eurozone == "yes"]
# sum that selection
sum(extra$Population[extra$Eurozone == "yes"])
```

</details>
  
  **9- Write extra into file ex6c_output.txt**
  
  *After each of the following steps, check the output file in the RStudio file browser (lower-right panel).*
  
  * Try with the default arguments.

<details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
write.table(extra, file="ex6c_output.txt")
```

</details>
  
  * Add the argument "row.names" set to FALSE.

<details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
write.table(extra, file="ex6c_output.txt", 
            row.names = FALSE)
```

</details>
  
  * Add the argument "quote" set to FALSE.

<details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
write.table(extra, file="ex6c_output.txt", 
            row.names = FALSE,
            quote = FALSE)
```

</details>
  
  * Add the argument "sep" set to "\t" or to ","

<details>
  <summary>
  *Answer*
</summary>
  
  ```{r, eval=F}
write.table(extra, file="ex6c_output.txt", 
            row.names = FALSE,
            quote = FALSE,
            sep="\t")
```

</details>
  