## Exercise 7. 

Create the script "exercise6.R" and save it to the "Rcourse/Module2" directory: you will save all the commands of exercise 7 in that script.
<br>Remember you can comment the code using #.


<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
getwd()
setwd("Rcourse/Module2")
setwd("~/Rcourse/Module2")
```

</details>

### Exercise 6a. Input / output

**1- Import the following file (use download.file() function) into your current working directory (Module2):**
https://data.cityofnewyork.us/resource/vfnx-vebw.csv


<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
download.file(url="https://data.cityofnewyork.us/resource/vfnx-vebw.csv", destfile="vfnx-vebw.csv")
```

</details>

**2- Check that the file you download is present in the current directory (use dir())**

**3- Read this file into object squirrels (remember that the read.csv function exists)**

This data set contains the census of NYC central park squirrels!

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
# with read.table
squirrels <- read.table("vfnx-vebw.csv", header=T, sep=",", as.is=TRUE)
# read.csv is an option
squirrels <- read.csv("vfnx-vebw.csv")
```

</details>

**4- Select only "Juvenile" squirrels ("Juvenile" in the "age" column). How many squirrels do you get?**

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
squirrels[squirrels$age == "Juvenile", ]
```

</details>

**5- Select squirrels if their primary fur color is "Cinnamon". How many squirrels do you get?**

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
squirrels[squirrels$primary_fur_color == "Cinnamon", ]
```

</details>

**6- Select squirrels that are both Juvenile and Cinnamon. How many squirrels are those? Write to a csv file.**

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
sqJC <- squirrels[squirrels$age == "Juvenile" & squirrels$primary_fur_color == "Cinnamon", ]
write.csv(sqJC, "squirrels_Juvenile_Cinnamon.csv", quote=FALSE, row.names=FALSE)
```

</details>

**7- Back to the main "squirrels" data frame: what are the most populated hectares?**

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
# use table to count occurrences of terms
table(squirrels[, "hectare"])
```

</details>

**8- How many squirrels are located in hectare 41B ? (see columns "hectare" and "hectare_squirrel_number")**

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
# select hectare 41B
hect41B <- squirrels[squirrels$hectare == "41B",]
# sum up values in the "hectare_squirrel_number" column
sum(hect41B[, "hectare_squirrel_number"])
```

</details>

**9- From the hectare 41B selected squirrels: what "primary fur color" does the squirrel found "chasing" displayed?**

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
hect41B[hect41B$chasing == "true", "primary_fur_color"]
```

</details>

