## Exercise 10: For loop

Create the script "exercise10.R" and save it to the "Rcourse/Module2" directory: you will save all the commands of exercise 10 in that script.
<br>Remember you can comment the code using #.


<details>
<summary>
correction
</summary>

```{r, eval=F}
getwd()
setwd("~/Rcourse/Module2")
```

</details>


**1- Write a for loop that iterates over the sequence of numbers 2 to 10 (both included), and prints the square root of each number (function sqrt()).**

<details>
<summary>
correction
</summary>

```{r}
for(i in 2:10){
	print(sqrt(i))
}
```

</details>


**2- Write a for loop that iterates over the sequence of numbers 5 to 15 (both included), and prints a new vector of 2 elements containing the number and its square root**

<details>
<summary>
correction
</summary>

```{r}
for(i in 5:15){
	veci <- c(i, sqrt(i))
        print(veci)
}
```

</details>

**3- Create the following matrix**

```{r}
mat1 <- matrix(rnorm(40), nrow=20)
```

* Write a for loop that iterates over each row of **mat1** and prints the **median value of each row**.

<details>
<summary>
correction
</summary>

```{r}
for(j in 1:nrow(mat1)){
	# extract the row
	rowj <- mat1[j,]
	# compute the median
	medrowj <- median(rowj)
	# print median value in row
	print(medrowj)
}  

# with less lines of code:
for(j in 1:nrow(mat1)){
	# print median value in row
	print(median(mat1[j,]))
}   
```     

</details>

**2- If statement in for loop**

Create the following matrix:

```{r}
mat4 <- matrix(c(2, 34, 1, NA, 89, 7, 12, NA, 0, 38),
	nrow=5)
```

Write a **for** loop that iterates over each row of **mat4**: **if** an **NA** is found, print the row number and the entire row where the **NA** is found.

<details>
<summary>
correction
</summary>

```{r}
for(k in 1:nrow(mat4)){
	# extract row
	rowk <- mat4[k,]
	if(any(is.na(rowk))){
		print(k)
		print(rowk)
	}
}
```

</details>

**3- For loop, if statement and regular expression**

Create vector **vec4** as:

```{r}
vec4 <- c("Oct4", "DEPP", "RSU1", "Hk2", "ZNF37A", "C1QL1", "Shh", "Cdkn2a")
```

**vec4** contains Human and Mouse gene symbols.
<br>

Loop over each element of **vec4**:

* If the element is a **human gene (both characters and numbers; all characters are written in upper-case)**, print a vector of two elements: the name of the gene and "human gene".<br>
* If the element is a **mouse gene (both characters and numbers; only the first character is written in upper-case)**, print a vector of two elements: the name of the gene and "mouse gene".<br>

> Tip 1: *Use grep and a regular expression in the if statement !*<br>
> Tip 2: *When grep does not find a match, it returns an element of **length 0** !*<br>
> Tip 3: *You can also use grepl: check the help page*

How do you get started?

* First, work on the regular expressions: how do you retrieve Human genes only? How do you retrieve Mouse genes only?
* Then, integrate the regular expressions in the if statement.
* Finally, integrate all this in a for loop!

<br>

<details>
<summary>
correction
</summary>

```{r}
for(gene in vec4){
	if(length(grep(pattern="^[A-Z0-9]+$", x=gene)) != 0){
		print(c(gene, "human gene"))
	}else if(length(grep(pattern="^[A-Z]{1}[a-z0-9]+$", x=gene)) != 0){
		print(c(gene, "mouse gene"))
	}
}

# With grepl
	# grepl returns a logical vector (match or not for each element of x), not the matching elements themselves.
for(gene in vec4){
        if(grepl(pattern="^[A-Z0-9]+$", x=gene)){
                print(c(gene, "human gene"))
        }else if(grepl(pattern="^[A-Z]{1}[a-z0-9]+$", x=gene)){
                print(c(gene, "mouse gene"))
        }
}

# easier way! whenever a lower case character is present: it is from mouse
for(gene in vec4){
        if(length(grep(pattern="[[:lower:]]", x=gene)) != 0){
                print(c(gene, "mouse gene"))
        }else{
                print(c(gene, "human gene"))
        }
}

```

</details>
