## Exercise 6. 

Create the script "exercise6.R" and save it to the "Rcourse/Module2" directory: you will save all the commands of exercise 6 in that script.
<br>Remember you can comment the code using #.


<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
getwd()
setwd("Rcourse/Module2")
setwd("~/Rcourse/Module2")
```

</details>

### Exercise 6a. Input / output

**1- Import the following file (use download.file() function: check the help page!) into your current working directyr (Module2)**
https://data.cityofnewyork.us/resource/vfnx-vebw.csv


<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
download.file(url="https://data.cityofnewyork.us/resource/vfnx-vebw.csv", destfile="vfnx-vebw.csv")
```

</details>

**2- Check that the file you download is present in the current directory (use dir())**

**3- Read this file into object squirrels (remember that the read.csv function exists)**

This data set contains the census of NYC central park squirrels!

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
# with read.table
squirrels <- read.table("vfnx-vebw.csv", header=T, sep=",", as.is=TRUE)
# read.csv is an option
squirrels <- read.table("vfnx-vebw.csv")
```

</details>

**4- Select only "Juvenile" squirrels ("Juvenile" in the "age" column). How many squirrels do you get?**

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
squirrels[squirrels$age == "Juvenile", ]
```

</details>

**5- Select squirrels if their primary fur color is "Cinnamon". How many squirrels do you get?**

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
squirrels[squirrels$primary_fur_color == "Cinnamon", ]
```

</details>

**6- Finally, select squirrels that are both Juvenile and Cinnamon. How many squirrels are those?**

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
squirrels[squirrels$age == "Juvenile" & squirrels$primary_fur_color == "Cinnamon", ]
```

</details>






