## Exercise 5. Data frame manipulation

Create the script "exercise5.R" and save it to the "Rcourse/Module1" directory: you will save all the commands of exercise 5 in that script.
<br>Remember you can comment the code using #.


<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
getwd()
setwd("Rcourse/Module1")
setwd("~/Rcourse/Module1")
```

</details>

### Exercise 5a

**1- Create the following data frame:**

| | | |
|:---:|:---:|:---:|
|43|181|M|
|34|172|F|
|22|189|M|
|27|167|F|

<br>
With Row names: **John, Jessica, Steve, Rachel**.
<br>
And Column names: **Age, Height, Sex**.

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
mydf <- data.frame(Age=c(43, 34, 22, 27), 
                 Height=c(181, 172, 189, 167),
                 Sex=c("M", "F", "M", "F"),
                 row.names = c("John", "Jessica", "Steve", "Rachel"),
                 stringsAsFactors=FALSE)
```

</details>

**2- Check the structure of mydf with str().**

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
str(mydf)
```

</details>

**3- Calculate the average/mean age and height in mydf.**

Try different approaches:

* Calculate the average for each column separately.

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
mean(mydf$Age)
mean(mydf$Height)
```

</details>

* Calculate the average of both columns simultaneously using the apply() function.

<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
# we have to remove the Sex column: we can calculate the average only with numbers
apply(mydf[,-3], 2, mean)
apply(mydf[,1:2], 2, mean)
apply(mydf[,-grep("Sex", colnames(mydf))], 2, mean)
```

</details>

**4- Change the row names of mydf so the data becomes anonymous:** 
Use Patient1, Patient2, etc. instead of actual names.

<details>
<summary>
*Answer*
</summary>

```{r, eval=F} 
rownames(mydf) <- c("Patient1", "Patient2", "Patient3", "Patient4")
# try also the paste function!
rownames(mydf) <- paste("Patient", 1:4, sep="")
```

</details>

**5- Create the data frame mydf2 that is a subset of mydf containing only the female entries.**
 
<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
# which elements are female ("F" in the "Sex" colum)
mydf$Sex=="F"
# retrieve rows that contain the female entries, and save in mydf2
mydf2 <- mydf[mydf$Sex=="F",]
```

</details>

**6- Create the data frame mydf3 that is a subset of mydf containing only entries of males taller than 170.**
 
<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
# which entries are males
mydf$Sex=="M"
# which entries are greater than 170 in column "Height"
mydf$Sex=="M" & mydf$Height > 170
# retrieve rows that contain the males that are taller than 170, and save in mydf3
mydf3 <- mydf[mydf$Sex=="M" & mydf$Height > 170,]
```

</details>


</details>
