## Exercise 9: If statement

Create the script "exercise9.R" and save it to the "Rcourse/Module2" directory: you will save all the commands of exercise 9 in that script.
<br>Remember you can comment the code using #.


<details>
<summary>
*Answer*
</summary>

```{r, eval=F}
getwd()
setwd("~/Rcourse/Module2")
```

</details>


**1- Create vector vec2 as:**


```{r}
vec2 <- c("kiwi", "apple", "pear", "grape")
```

* Use an **if** statement and the **%in%** function to check whether "apple" is present in vec2 (in such case print "there is an apple!")

<details>
<summary>
*Answer*
</summary>

```{r}
if("apple" %in% vec2){
	print("there is an apple there")
}
```

</details>

* Use an **if** statement and the **%in%** function to check whether "grapefruit" is present in vec2: if "grapefruit" is not found, test whether "pear" is found (using **else if**).

<details>
<summary>
*Answer*
</summary>

```{r}
if("grapefruit" %in% vec2){
        print("there is a grapefruit here")
}else if("pear" %in% vec2){
	print("there is no grapefruit here, but there is a pear!")
}
```

</details>

* Add an **else** section in case neither grapefruit nor pear is found in vec2.<br>
Test your **if** statement also on **vec3**:

```{r}
vec3 <- c("cherry", "strawberry", "blueberry", "peach")
```

<details>
<summary>
*Answer*
</summary>

```{r}
if("grapefruit" %in% vec2){
        print("there is a grapefruit here")
}else if("pear" %in% vec2){
	print("there is no grapefruit here, but there is a pear!")
}else{
	print("no grapefruit and no pear can be found")
}
```

</details>





