## Exercise 4. Matrix manipulation

Create the script "exercise4.R" and save it to the "Rcourse/Module1" directory: you will save all the commands of exercise 4 in that script.
<br>Remember you can comment the code using #.

<details>
<summary>
correction
</summary>

```{r, eval=F}
getwd()
setwd("Rcourse/Module1")
setwd("~/Rcourse/Module1")
```

</details>

**1- Create the matrix mat as:**

```{r}
mat <- matrix(c(seq(from=1, to=10, by=2), 5:1, rep(x=2020, times=5)), ncol=3)
```

What does function seq() do?

<details>
<summary>
correction
</summary>

**seq** generate sequences of numbers. Here, it creates a sequences from 1 to 10 with a step of 2 numbers.

</details>

**2- What are the dimensions of mat (number of rows and number of columns)?**

<details>
<summary>
correction
</summary>

```{r}
# number of rows
nrow(mat)
# number of columns
ncol(mat)
# dimensions: number of rows, number of columns
dim(mat)
```

</details>

**3- Extract the first row of mat. Then the third column.**

<details>
<summary>
correction
</summary>

```{r}
# first row:
mat[1,]
# third column
mat[,3]
```

</details>

**4- Calculate the sum of each row, and the sum of each column**

<details>
<summary>
correction
</summary>

```{r}
rowSums(mat); colSums(mat)
```

</details>

**5- Add column names to mat: "day", "month" and "year", respectively.**

<details>
<summary>
correction
</summary>

```{r}
colnames(mat) <- c("day", "month", "year")
```

</details>

**6- Add row names to mat: letters "A" to "E"**

<details>
<summary>
correction
</summary>

```{r}
rownames(mat) <- c("A", "B", "C", "D", "E")
rownames(mat) <- LETTERS[1:5]
```

</details>

**7- Shows row(s) of mat where the month column is greater than or equal to 3.**

<details>
<summary>
correction
</summary>

Step by step:
```{r}
# select column month
mat[, "month"]
# element(s) of column month that is (are) greater than or equal to 3
mat[,"month"] >= 3
# finally select row(s) where the month columns is greater than or equal to 3
mat[mat[,"month"] >= 3,]
```

</details>

**8- Shows row(s) of mat where the month column is greater than or equal to 3 AND the day column is less than 5. How many rows are left ?**

<details>
<summary>
correction
</summary>

Step by step:
```{r}
# select column month
mat[, "month"]
# element(s) of column month that is/are greater than or equal to 3
mat[,"month"] >= 3
# element(s) of column day that is/are less than 5
mat[,"day"] < 5
# element(s) of column month that is/are greater than or equal to 3 AND element(s) of column day that is/are less than 5
mat[,"month"] >= 3 & mat[,"day"] < 5
# finally select corresponding rows
mat[mat[,"month"] >= 3 & mat[,"day"] < 5,]
```

</details>
