## Exercice 1. Getting started ~ 10 minutes

Create the script "exercise1.R" (in R Studio: File -> New File) and save it to the "Rcourse/Module1" directory: you will save all the commands of exercise 1 in that  script.
<br>Remember you can comment the code using #.

**1- From the console, go to Rcourse/Module1.
First check where you currently are with getwd(); 
then go to Rcourse/Module1 with setwd()**.
Remember that **~** is a shortcut to your home directory.

<details>
<summary>
correction
</summary>

```{r, eval=FALSE}
getwd()
setwd("Rcourse/Module1")
setwd("~/Rcourse/Module1")
```

</details>


**2- Using R as a calculator, calculate the square root of 654 (don't know the function? Search the internet!).**

<details>
<summary>
correction
</summary>

```{r}
sqrt(654)
```

</details>

**3- Create a new object "myobject" that contains value 60.
Show "myobject" in the console.**

<details>
<summary>
correction
</summary>

```{r}
myobject <- 60
myobject
```

</details>

**4- Subtract 1 from myobject. Reassign.**

<details>
<summary>
correction
</summary>

```{r}
myobject <- myobject - 1
```

</details>

**5- Create a new object "mysqrt" that will store the square root of "myobject".**

<details>
<summary>
correction
</summary>

```{r}
mysqrt <- sqrt(myobject)
```

</details>

**6- Create a new object "mydiv" that will store the result of "myobject" divided by "mysqrt".**

<details>
<summary>
correction
</summary>

```{r}
mydiv <- myobject / mysqrt
```

</details>

