## Exercise 6. 

Create the script "exercise6.R" and save it to the "Rcourse/Module2" directory: you will save all the commands of exercise 6 in that script.
<br>Remember you can comment the code using #.


<details>
<summary>
correction
</summary>

```{r, eval=F}
getwd()
setwd("Rcourse/Module2")
setwd("~/Rcourse/Module2")
```

</details>

### Exercise 6a. Input / output

**1- Download folder "i_o_files" in your current directory with:** 

```{r, eval=F}
# system invokes the OS command specified by the "command" argument.
system(command="svn export https://github.com/biocorecrg/CRG_RIntroduction/trunk/i_o_files")
```

All files that will be used for exercise 6 are found in the **i_o_files** folder ! 

**2- Read in the content of ex6a_input.txt using the scan command; save in object z**

How many elements are in z?

<details>
<summary>
correction
</summary>

```{r, eval=F}
# scan content of the file
z <- scan("i_o_files/ex6a_input.txt")
# number of elements (length of vector)
length(z)
```

</details>

**3- Sort z: save sorted vector in object "zsorted". ?sort**

<details>
<summary>
correction
</summary>

```{r, eval=F}
zsorted <- sort(z)
```

</details>

**4- Write zsorted content into file ex6a_output.txt. ?write**

<details>
<summary>
correction
</summary>

```{r, eval=F}
write(zsorted, "ex6a_output.txt")
```

</details>

**5- Check the file you produced in the RStudio file browser (click on the file in bottom-right panel, "Files" tab). Save the content of zsorted again but this time setting the argument "ncolumns" to 1: how does the file look now?**

<details>
<summary>
correction
</summary>

```{r, eval=F}
write(zsorted, "ex6a_output.txt", ncolumns=1)
```

</details>

### Exercise 6b - I/O on data frames: play with the arguments of read.table
  
**1- field separator**

* **Read ex6b_IO_commas_noheader.txt in object fs. ?read.table.
What are the dimensions of fs?**

<details>
<summary>
correction
</summary>

```{r, eval=F}
# read in file with default parameters
fs <- read.table("i_o_files/ex6b_IO_commas_noheader.txt")
dim(fs)
```

</details>

* **Fields/columns are separated by commas: change the default value of the "sep" argument and read in the file again.
What are now the dimensions of fs?**

<details>
<summary>
correction
</summary>

```{r, eval=F}
# change field separator to ","
fs <- read.table("i_o_files/ex6b_IO_commas_noheader.txt", 
	sep=",")
dim(fs)
```

</details>

**2- field separator + header**

* **Read ex6b_IO_commas_header.txt in object fs_c.
What are the dimensions of fs_c ?**

<details>
<summary>
correction
</summary>

```{r, eval=F} 
fs_c <- read.table("i_o_files/ex6b_IO_commas_header.txt")
dim(fs_c)
```

</details>

* **Check head(fs_c) and change the default field separator to the appropriate one.**

<details>
<summary>
correction
</summary>

```{r, eval=F}
fs_c <- read.table("i_o_files/ex6b_IO_commas_header.txt", 
                   sep=",")
```

</details>

* **The first row should to be the header (column names)! Change the default value of the header parameter and read in the file again.**
What are now the dimensions of fs_c ?

<details>
<summary>
correction
</summary>

```{r, eval=F}
fs_c <- read.table("i_o_files/ex6b_IO_commas_header.txt", 
                   sep=",", 
                   header=TRUE)
```

</details>

**3- skipping lines**

* **Read ex6b_IO_skip.txt in object sk.**

<details>
<summary>
correction
</summary>

```{r, eval=F, message=F, warning=F, error=F}
sk <- read.table("i_o_files/ex6b_IO_skip.txt")
```

</details>

**Is R complaining ?**<br>
 
Check "manually" the file (open it in the R Studio file browser).<br>

* The "skip" argument allows you to ignore one or more line(s) before reading in a file. **Introduce this argument with the appropriate number of lines to skip, and read in the file again.**<br>

<details>
<summary>
correction
</summary>

```{r, eval=F}
sk <- read.table("i_o_files/ex6b_IO_skip.txt",
                 skip=2)
dim(sk)
```

</details>

* Is R still complaining? 
What are now the dimensions of sk ?

* **Change the default field separator.**
What are now the dimensions of sk ?

<details>
<summary>
correction
</summary>

```{r, eval=F}
sk <- read.table("i_o_files/ex6b_IO_skip.txt",
                 skip=2,
                 sep=",",
                 header=T)
```

</details>

**4- Comment lines**

* **Read ex6b_IO_comment.txt in object cl.**

<details>
<summary>
correction
</summary>

```{r, eval=F, warning=F, message=F, error=F}
cl <- read.table("i_o_files/ex6b_IO_comment.txt")
```

</details>

Is R complaining again ? **Check manually the file and try to find out what is wrong...**<br>

What is the "comment.char" argument used for ? **Adjust the comment.char argument and read in the file again.**

<details>
<summary>
correction
</summary>

```{r, eval=F}
cl <- read.table("i_o_files/ex6b_IO_comment.txt",
                 comment.char = "*")
```

</details>

* **Adjust also the header and sep arguments to read in the file correctly.**
What are now the dimensions of cl?

<details>
<summary>
correction
</summary>

```{r, eval=F}
cl <- read.table("i_o_files/ex6b_IO_comment.txt",
                 comment.char = "*",
                 sep=",",
                 header=TRUE)
dim(cl)
```

</details>

**4- final**

* **Read ex6b_IO_final.txt in object "fin".**

<details>
<summary>
correction
</summary>

```{r, eval=F, warning=F, error=F, message=F}
fin <- read.table("i_o_files/ex6b_IO_final.txt")
```

</details>

* **Adjust the appropriate arguments of "write.table" according to what you have learnt so far, in order to obtain the data frame "fin" of dimensions 167 x 4.**

<details>
<summary>
correction
</summary>

```{r, eval=F}
fin <- read.table("i_o_files/ex6b_IO_final.txt",
                  sep=",",
                  header=TRUE,
                  skip=3,
                  comment.char="&"
                  )
```

</details>




